Word-Referent Identification Under Multimodal Uncertainty

### 2018-04-20 Writeup/ms.Rmd
minor

Some previous research found a similar case of suboptimal behavior. For instance, studies that explored  the identification of ambiguous, newly learned pairs of word-referent associations all reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].  Recently, @hofer2017 provided a probabilistic model of this phenomenon. In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality. Our finding, besides providing more evidence to this documented fact, suggests that the apparent reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.

>>>>

Some previous research found a similar case of suboptimal behavior. For instance, studies that explored  the identification of ambiguous, newly learned pairs of word-referent associations all reported what appears to be a decrease in speech perception acuity in both children [@stager1997] and adults [@pajak2016].  Recently, @hofer2017 provided a probabilistic model of this phenomenon. In agreement with the method and finding in the current study, @hofer2017 characterized the apparent reduction in perceptual acuity as an increase in the noise variance of the auditory modality. Our finding, besides providing more evidence to this documented fact, suggests that the  reduction in perceptual acuity may occurs simultaneously in both the auditory *and* the visual modalities.
